 \documentclass[10pt]{article}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{color}
\usepackage{listings}
\usepackage{a4wide}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[hang,small]{caption}
\usepackage{setspace}
\usepackage{algorithmic}%% For the Algorithms.
\usepackage{algorithm}
\lstset{frame=shadowbox, rulesepcolor=\color{blue}}
\usepackage{versions}
\excludeversion{INUTILE}
%\excludeversion{LONG}\excludeversion{VLONG}\includeversion{SHORT}
\includeversion{LONG}\excludeversion{SHORT}\includeversion{VLONG}
\markversion{TODO}
\markversion{TODOSRINIVAS}
\excludeversion{TODOSRINIVAS}
\excludeversion{TODO}

\newtheorem{corollary}{Corollary}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

\begin{titlepage}
\title{Thesis proposal: \\Synergistic Analysis of Algorithms and Data Structures.}
\author{Carlos Ochoa$^{1}$
  \\\\\\\\\underline{\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \
    \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ }
  \\Advisor: J\'er\'emy Barbay$^1$\\\\\\\\
  $^1$ Departamento de Ciencias de la Computaci\'on (DCC),\\ Universidad de Chile, Santiago, Chile.
}
\date{\today}
\newtheorem*{thma}{Proposition}
\end{titlepage}
\begin{document}
%\doublespacing
\maketitle
\begin{abstract}
  Karp et al. (1988) described Deferred Data Structures for Multisets
  as ``lazy'' data structures which partially sort data to support
  online rank and select queries, with the minimum amount of work in
  the worst case over instances of size $n$ and number of queries $q$
  fixed (i.e., the query size). Barbay et al. (2016) refined this
  approach to take advantage of the gaps between the positions hit by
  the queries (i.e., the structure in the queries). We develop new
  techniques in order to further refine this approach and to take
  advantage all at once of the structure (i.e., the multiplicities of
  the elements), the local order (i.e., the number and sizes of runs)
  and the global order (i.e., the number and positions of existing
  pivots) in the input; and of the structure and order in the sequence
  of queries. Our main result is a synergistic deferred data structure
  which performs much better on large classes of instances, while
  performing always asymptotically as good as previous solutions. As
  intermediate results, we describe two new synergistic sorting
  algorithms, which take advantage of the structure and order (local
  and global) in the input, improving upon previous results which take
  advantage only of the structure (Munro and Spira 1979) or of the
  local order (Takaoka 1997) in the input; and one new multiselection
  algorithm which takes advantage of not only the order and structure
  in the input, but also of the structure in the queries.  We
  described two compressed data structures to represent a multiset
  taking advantage of both the local order and structure, while
  supporting the operators \texttt{rank} and \texttt{select} on the
  multiset.
\end{abstract}
\clearpage

\input{proposal}

\bibliographystyle{plain}
\bibliography{bibliographyDatabaseJeremyBarbay,publicationsJeremyBarbay,addedForThePaper}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
